\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
 
\urlstyle{same}

\begin{document}

\name{Frank R. Edwards \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}

CLJ 578B   & {\it Office:}  973.353.3348 \\
123 Washington St & {\it Email:} frank.edwards@rutgers.edu\\
Newark, NJ 07102-3094 &  {\it Web:} f-edwards.github.io\\
\end{tabular}

\section{\sc Employment and Affiliations}

\textsc{Rutgers University - Newark}
\begin{list1}
\item[] Assistant Professor. School of Criminal Justice. 2018 - 
\item[] Affiliate Faculty. Department of Sociology and Anthropology 2021 - 
\end{list1}

\textsc{The University of Washington}
\begin{list1}
\item[] Center for Studies in Demography and Ecology. Regional Affiliate. 2020 - 
\end{list1}

\textsc{Cornell University}
%\vspace*{.1in}
\begin{list1}
\item[] Postdoctoral Associate. Bronfenbrenner Center for Translational Research. 2017 - 2018
\item[] Research Associate: National Data Archive on Child Abuse and Neglect. 2018 - 
\end{list1}

\section{\sc Education}
\textsc{Ph.D., Sociology. The University of Washington. 2017}
%\vspace*{.1in}
% \begin{list1}
% \item[] Concentration in social statistics
% \item[] Committee: Hedwig Lee, Jake Rosenfeld, Alexes Harris, Christopher Wildeman, Heather Hill
% \end{list1}

\textsc{M.A., Sociology. DePaul University. 2012}

\textsc{B.A., Sociology and History, The University of Texas at Austin. 2005}

% \section{\sc Interests} 

% Social control, race, health, children and families, political sociology, welfare state, applied Bayesian statistics, data visualization, multilevel data analysis

\section{\sc Peer reviwed articles and chapters}

\textbf{Edwards, Frank R.}, Kelley Fong, Victoria Copeland, Mical Raz, and Alan Dettlaff. Forthcoming. ``Administrative Burdens in Child Welfare''. \textit{The Russell Sage Foundation Journal of The Social Sciences}.

Horowitz, Veronia, Kimberly Spencer-Suarez, Ryan Larson, Robert Stewart, \textbf{Frank R. Edwards}, Emmi Obara, and Christopher Uggen. Forthcoming. ``Dual Debtors: Child Support and Criminal Legal Financial Obligations''. \textit{Social Service Review}.

\textbf{Edwards, Frank R.}, Sarah Wakefield, Kieran Healy, and Christopher Wildeman. 2021. ``Child Protective Services Contact in the 20 Most Populous Counties in the US''. \textit{Proceedings of the National Academy of Sciences} (\href{https://www.pnas.org/content/118/30/e2106272118}{html})

\begin{itemize}
  \item Covered by \textit{The PBS News Hour}, \textit{The Dallas Morning News}, \textit{ProPublica}, \textit{The Washington Post}, and other outlets
\end{itemize}

Raz, Mical, Alan Dettlaff, and \textbf{Frank R. Edwards}. 2021. ``The Perils of Child `Protection' for Children of Color: Lessons from History''. \textit{Pediatrics}.

Yi, Youngmin, \textbf{Frank R. Edwards}, and Christopher Wildeman. 2020. ``Cumulative Prevalence of Confirmed Maltreatment and Foster Care Placement for US Children by Race/Ethnicity, 2011 - 2016.'' \textit{American Journal of Public Health} 110(5):704-709. (\href{https://ajph.aphapublications.org/doi/abs/10.2105/AJPH.2019.305554}{html})

\begin{itemize}
	\item Selected for inclusion in the American Public Health Association's Continuing Medical Education program
\end{itemize}

Wildeman, Christopher, \textbf{Frank R. Edwards}, and Sara Wakefield. 2020. ``The Cumulative Prevalence of Termination of Parental Rights for U.S. Children, 2000-2016''. \textit{Child Maltreatment} 25(1):32-42. (\href{https://doi.org/10.1177/1077559519848499}{html})

\begin{itemize}
  \item Article of the year, \textit{Child Maltreatment} editorial board
\end{itemize}

\textbf{Edwards, Frank R.}, Hedwig Lee, and Michael Esposito. 2019. ``Risk of being killed by police use of force in the United States by age, race–ethnicity, and sex''. \textit{Proceedings of the National Academy of Sciences} 116 (34):16793-16798. (\href{https://www.pnas.org/content/116/34/16793}{html})

\begin{itemize}
  \item Covered by \textit{The New York Times}, \textit{The Washington Post}, \textit{The Los Angeles Times}, \textit{USA Today}, \textit{The PBS News Hour}, \textit{NPR}, \textit{The Root}, \textit{Vox}, \textit{NBC News}, \textit{CBS News}, \textit{Scientific American}, \textit{Le Monde} and other outlets.
  \item Cited in Senate testimony in support of the Justice in Policing Act of 2020 by Senator Chuck Schumer. Cited in promotional materials for the Justice in Policing Act of 2020 by Vice President Kamala Harris and Senator Cory Booker. Cited on social media by Representative Alexandria Ocasio-Cortez and secretary Julián Castro. 
\end{itemize} 

Fernandes, April, \textbf{Frank R. Edwards}, Michele Cadigan, and Alexes Harris. 2019. ``Monetary Sanctions: A Review of Revenue Generation, Legal Challenges, and Reform''. \textit{Annual Review of Law and Social Science} 15(1):397-413. (\href{https://www.annualreviews.org/doi/abs/10.1146/annurev-lawsocsci-101518-042816}{html})

\textbf{Edwards, Frank R.} 2019. ``Family Surveillance: Police and the Reporting of Child Abuse and Neglect.'' \textit{The Russell Sage Foundation Journal of The Social Sciences} 5(1):50-70. (\href{https://www.rsfjournal.org/content/5/1/50}{html})

\textbf{Edwards, Frank R.}, Michael Esposito, and Hedwig Lee. 2018. ``Risk of Police-Involved Death by Race/Ethnicity and Place, United States, 2012-2018''. \textit{The American Journal of Public Health} 108(9):1241-1248. (\href{https://ajph.aphapublications.org/doi/10.2105/AJPH.2018.304559}{html})

\begin{itemize}
  \item Covered by \textit{Newsweek}, \textit{The Boston Globe}, \textit{Salon}, \textit{The Atlantic}, \textit{The Independent}, \textit{People}, \textit{CBS News}, and other outlets.
\end{itemize}

\textbf{Edwards, Frank R.} and Christopher Wildeman. 2018. ``Characteristics of the Frontline Child Welfare Workforce.'' \textit{Children and Youth Services Review} 89:13-26. (\href{https://osf.io/a86td/}{pdf})

Martin, Karin, Sarah Shannon, Bryan Sykes, \textbf{Frank R. Edwards}, and Alexes Harris. 2018. ``Monetary Sanctions in Criminal Justice.'' \textit{Annual Review of Criminology} 1(1):471-495. (\href{http://frankedwards.net/wp-content/uploads/2018/01/annurev-criminol-032317-091915.pdf}{pdf})

Harris, Alexes and \textbf{Frank R. Edwards}. 2017. ``Fines and Monetary Sanctions.'' \textit{Oxford Research Encyclopedia of Criminology and Criminal Justice}. 

\textbf{Edwards, Frank R.} 2016. ``Saving Children, Controlling Families: Punishment, Redistribution and Child Protection.'' \textit{American Sociological Review} 81(3):575-595. (\href{http://frankedwards.net/wp-content/uploads/2016/03/savingchildren.pdf}{pdf})

\begin{itemize}
  \item Outstanding graduate student paper, American Sociological Association Section on Children and Youth
  \item Outstanding graduate student paper, American Sociological Association Family Section
  \item Covered by \textit{The Arkansas Times} and \textit{LSE American Politics and Policy Blog}
\end{itemize}

\textbf{Edwards, Frank R.} 2014. ``Framing Punishment: Expert Selection and Punitive Ideology in the News.'' \textit{McGill Sociological Review} 4:93-112. (\href{https://www.mcgill.ca/msr/msr-volume-4/framing-punishment}{html}) 

\section{\sc Law Reviews}

Rocha Beardall, Theresa and \textbf{Frank R. Edwards}. 2021. ``Abolition, Elimination, and Indian Child Welfare.'' \textit{Columbia Journal of Race and Law}. 11(3). (\href{https://osf.io/preprints/socarxiv/mqgtc/}{html})

\begin{itemize}
  \item 2022 John Hope Franklin Prize for the best article on race, racism and the law, Law and Society Assocaition.
\end{itemize}

\textbf{Edwards, Frank R.} 2020. ``Fiscal Pressures, the Great Recession, and Monetary Sanctions in Washington Courts of Limited Jurisdiction.'' \textit{The UCLA Criminal Justice Law Review} 4(1). (\href{https://escholarship.org/content/qt8h95m64x/qt8h95m64x.pdf}{pdf})

\begin{itemize}
\item Covered by \textit{City Lab}.
\end{itemize}

\section{\sc Policy reports, commentary, and other writing}

\textbf{Edwards, Frank R.} Book review: \textit{Trapped in a Maze: How Social Control Institutions Drive Family Poverty and Inequality} by Leslie Paik. 2022. Social Forces. (\href{https://academic.oup.com/sf/advance-article-abstract/doi/10.1093/sf/soac024/6551084}{html})

\textbf{Edwards, Frank R.} and Theresa Rocha Beardall. 2021. ``Mechanisms of American Indian and Alaska Native Inequality in Child Welfare Across U.S. States''. Prepared for Casey Family Programs. (\href{https://osf.io/preprints/socarxiv/fcz5p/}{html})

Raz, Mical and \textbf{Frank R. Edwards}. 2020. ``Preventing Child Abuse Is Paramount, But Not a Reason to Open Schools''. \textit{Teachers College Record}. (\href{https://www.tcrecord.org/Content.asp?ContentID=23431}{html})

Esposito, Michael, \textbf{Frank Edwards}, and Hedwig Lee. 2020. ``The Demography of Police-Involved Homicides''. The American Sociological Association. \textit{ASA Footnotes} (\href{https://www.asanet.org/news-events/footnotes/jul-aug-2020/features/demography-police-involved-homicides}{html})

Lee, Hedwig, Michael Esposito, \textbf{Frank Edwards}, Yung Chun, and Michal Grinstein-Weiss. 2020. ``The Demographics of Racial Inequality in the United States''. The Brookings Institution, \textit{Up Front}. (\href{https://www.brookings.edu/blog/up-front/2020/07/27/the-demographics-of-racial-inequality-in-the-united-states/}{html}) 

\textbf{Edwards, Frank R.} and Alexes Harris. 2020. ``Legal Financial Obligations in Seattle Municipal Court''. Seattle, WA: City of Seattle Office for Civil Rights.

\textbf{Edwards, Frank R.} and April Fernandes. 2017. ``Monetary Sanctions in Washington''. In \textit{Monetary Sanctions in the Criminal Justice System}. Washington, DC: Laura and John Arnold Foundation.

\textbf{Edwards, Frank R.}, Mary Joyce, and Philip Howard. 2013. \textit{Digital Activism and Non-Violent Conflict}. Seattle, WA: University of Washington.

Kaba, Mariame and \textbf{Frank R. Edwards}. 2012. \textit{Policing Chicago Public Schools: A Gateway to the School-to-Prison Pipeline}. Chicago, IL: Project NIA.

\section{\sc Grants and contracts}

``Understanding sources of American Indian and Alaska Native inequality in child welfare system outcomes''. Casey Family Programs. Role: PI with Theresa Rocha-Beardall. 2022. \$40,000

``Guaranteed Income Experiment: Child Protection Outcomes.'' Redlich Horwitz Foundation. Role: Co-I with Zoe Bouchelle; Amy Castro and Stacia West PI. 2022-2025. \$261,089

``Dual Debt: Understanding the Relationship between Legal Financial Obligations and Child Support Debt.'' Arnold Ventures. Role: Co-I with Robert Stewart, Veronica Horowitz, Kimberly Spencer-Suarez, and Ryan Larson; Chris Uggen PI. 2021 - 2024. \$486,025 

``Understanding sources of American Indian and Alaska Native inequality in child welfare system outcomes''. Casey Family Programs. Role: PI with Theresa Rocha-Beardall. 2021. \$40,000

``Tribes and Families: Fulfilling the Dual-Promise of Indian Child Welfare Reform''. William T. Grant Foundation. Role: PI with Theresa Rocha Beardall. 2021 - 2024. \$518,546

``Mechanisms of American Indian and Alaska Native inequality in child welfare case processing across US States''. Casey Family Programs. Role: PI with Theresa Rocha Beardall. 2020. \$40,000 

``An Analysis of Court Imposed Monetary Sanctions in Seattle Municipal Courts, 2000-2017''. Role: Co-I, Alexes Harris PI. City of Seattle, Office for Civil Rights. 2018 - 2019. 

Research associate. National Data Archive on Child Abuse and Neglect. Role: Statistical consulting, training, and software development. 2018 - 2022

``Spatial variation in child welfare system contact''. Casey Family Programs. Role: Co-I, Chris Wildeman PI. 2018 - 2019

``Dual Debtors: Child Support and Criminal Financial Legal Obligations.''  Institute for Research on Poverty, University of Wisconsin. Role: Co-I, Chris Uggen PI. 2018 - 2019

``Left Behind: Deportation, Child Welfare and Foster Care Placements.'' Cornell Project 2Gen Pilot Studies Program. Role: Co-I, Matt Hall PI. 2017

\section{\sc Awards and Fellowships}

Early Career Faculty Fellow. Institute for the Study of Global Racial Justice, Rutgers University. 2021 - 2022

Presidential Dissertation Fellowship. The Graduate School, University of Washington. 2016

Herbert L. Costner Distinguished Graduate Student Paper Award, Department of Sociology, University of Washington. 2016

Prize in Public Interest Communications Research for \textit{Digital Activism and Non-Violent Conflict}. College of Journalism and Communications, University of Florida. 2014

\section{\sc Presentations}

``Assessing the Landscape: The Measurement and Modeling of Structural Racism, Novel Approaches to Administrative and Crowd-Sourced Data''. Invited presentation. Committee on Population, National Academy of Sciences. 2022.

``Keeping Families Together''. Invited Panelist. Our Sister Our Brother. Phoenix, AZ. 2022.

``Agents of Empire: Social Control in Indian Country''. Invited presentation. Centre for Criminological Research. University of Alberta. 2022.

``Geography and Institutional Drivers of American Indian and Alaska Native Inequality Across States''. Workshop. Protecting Our Children Conference. National Indian Child Welfare Association. 2022.

``Disrupting Health Disparities: Thinking Critically about Race''. Invited Panelist. Institute for the Study of Global Racial Justice. Rutgers University. 2022.

``Abolition and Indian Child Welfare''. Invited presentation with Theresa Rocha Beardall. Strengthened Bonds: Abolishing the Child Welfare System and Re-Envisioning Child Well-Being. Columbia Journal of Race and Law. 2021.

``Public Systems Compounding Oppression: International Exchange''. Invited panelist. Kempe Center for the Prevention and Treatment of Child Abuse and Neglect. University of Colorado. 2021.

``Policing, Justice and Community Safety, a Year after the Killing of George Floyd''. Invited panelist. Annenberg Center for Health Journalism. University of Southern California. 2021.

``VCIS Data and Special Populations''. National Data Archive on Child Abuse and Neglect. 2021.

``American Indian Inequality in Child Welfare System Contact in Minnesota''. Invited presentation. University of Minnesota - Duluth. 2021.

``Linking administrative and population data''. National Data Archive on Child Abuse and Neglect. 2021.

``Police violence in Washington State''. Invited presentation. Washington Advisory Committee to the U.S. Commission on Civil Rights. 2021.

``Risk of Being Killed by Police use of Force in the United States.'' Invited presentation. Chancellor's Research Day. Rutgers - Newark. 2021.

``Mechanisms of Alaska Native and American Indian inequality in child welfare case processing across US States''. Invited presentation. In Casey Family Programs Indian Child Welfare Group. 2021.

``Mechanisms of Alaska Native and American Indian inequality in child welfare case processing in Alaska''. Invited presentation. Alaska Tribal State Collaboration Group. 2021.

``Risk of Child Welfare System Contact by US State.'' Association for Public Policy Analysis and Management. 2020. 

``An Analysis of Court Imposed Monetary Sanctions in Seattle Municipal Court.'' Invited presentation. Seattle City Council. 2020.

``Police Violence in Indian Country.'' American Sociological Association. 2020.

``Sovereign Shields: Family Separation in Indian Country.'' Eastern Sociological Society. 2020.

``Risk of Being Killed by Police use of Force in the United States by Age, Race–Ethnicity, and Sex.'' American Society of Criminology. 2019.

``Sovereign Shields and State Violence in Indian Country.'' Invited presentation. American Indian Studies Department, San Francisco State University. 2019.

``Fiscal pressures, the Great Recession, and Washington courts of limited jurisdiction.'' Invited presentatioin. Progressing Reform of Fees and Fines: Towards A Research and Policy Agenda. Criminal Justice Policy Program, Harvard Law School. 2019.

``Sovereign Shields: Law Enforcement and State Violence in Indian Country.'' Native American and Indigenous Studies Association. 2019

``Sovereign Shields: Law Enforcement and State Violence in Indian Country.'' Law and Society Association. 2019

``Risk of Being Killed by Police Use-of-Force in the U.S. by Age, Race/Ethnicity, and Sex.'' Population Association of America. 2019

``Risk of Police-Involved Death by Race/Ethnicity and Place, United States, 2012-2018.'' American Sociological Association. 2018

``Characteristics of the Front-Line Child Welfare Workforce.'' Invited presentation. Casey Family Programs Child Welfare Data Leaders Meeting, plenary. 2018

``Family Surveillance: Police and the Reporting of Child Abuse and Neglect.'' Russell Sage Foundation. 2017

``Family Surveillance: Police and the Reporting of Child Abuse and Neglect.'' American Sociological Association. 2017

``Concentrated Social Control and Racial Inequality in Child Protection.'' American Sociological Association. 2016

``Saving Children, Controlling Families: Punishment, Redistribution, and Child Protection.'' Invited presentation. West Coast Poverty Center. University of Washington. 2016

``Saving Children, Controlling Families: Punishment, Redistribution, and Child Protection.'' American Sociological Association. 2015

``State Infrastructure and Child Welfare Surveillance.'' Society for the Study of Social Problems. 2015

``Digital Activism and Non-Violent Conflict.'' Invited presentation. Public Interest Communications Conference, Department of Journalism and Communication, University of Florida. 2014

``Race, Place, and Disparities in Foster Care Entries.'' West Coast Law and Society Retreat, University of Washington. 2013

``Punitive Juvenile Justice and Youth Crime Journalism: Chicago 1981-1982.'' Midwest Sociological Society. 2011

\section{\sc Advising}

\textsc{Rutgers University - Newark}

\begin{list1}
  \item[]Advisor: Ihsan Al-Zouabi
  \item[]Committee: Sadaf Hashimi, Lorena Avila, Vijay Chillar
\end{list1}

\section{\sc Teaching}

\textsc{Rutgers University - Newark}

\begin{list1}
  \item[]Introductory Statistics, PhD 
  \item[]Intermediate Statistics, PhD 
  \item[]Advanced Statistics: Bayesian, PhD
\end{list1}

\textsc{The University of Washington}
\begin{list1}

  \item[]Introduction to Sociology. 
  \item[]Department of Sociology Writing Instructor. 
  \item[]Teaching Assistant: Criminology; Sociological Theory; Introduction to Law; Societies and Justice; Drugs and Society.

\end{list1}

\textsc{DePaul University}

\begin{list1}

  \item[] Introduction to Sociology.

\end{list1}

\section{\sc Professional Service}

Occasional reviewer: \textit{American Journal of Public Health}, \textit{Journal of Policy Analysis and Management}, \textit{American Sociological Review}, \textit{American Journal of Sociology}, \textit{Journal of Public Administration Research and Theory}, \textit{Social Problems}, \textit{Criminology}, \textit{Child Welfare}, \textit{Science Advances}, \textit{Epidemiology}, \textit{The Lancet}, \textit{Journal of Research in Crime and Delinquency}, \textit{Proceedings of the National Academy of Sciences}, \textit{Demography}, \textit{PNAS-Nexus}, \textit{Social Forces}, \textit{Science}

Committee work (Rutgers School of Criminal Justice): PhD program committee, 2019 - 2022; MA program committee, 2018 - 2021; Faculty search committee, 2021

Conference session presider or discussant: American Sociological Association 2018, 2019, 2020, 2022 Population Association of America 2019, International Society for the Prevention of Child Abuse and Neglect Conference 2022.

Student advisory editor: \textit{Social Problems}. 2013-2014

\end{resume}
\end{document}
